ArKanjo: a tool for detecting function-level Code Duplication in the Linux Kernel

### 2025-06-19 paper/paper.tex
fix the number of graduate students

We conducted a multi-part ethnographic study to assess whether the duplications found by the ArKanjo tool were actionable. In the second semester of 2024 and the first semester of 2025, respectively, the main author, conducting a first validation, and 12 student groups (19 undergraduate and 6 graduate students) from the Free Software Development course at the University of São Paulo acted as new contributors to the Linux kernel in a broader experiment, used the tool to identify duplications within the Industrial I/O (IIO) subsystem and the AMD Display driver subsystem refactored the code to address the issues, and submitted their proposed fixes as patches to the community maintainers. The students documented their refactoring approaches and experiences interacting with the kernel community throughout this process.

>>>>

We conducted a multi-part ethnographic study to assess whether the duplications found by the ArKanjo tool were actionable. In the second semester of 2024 and the first semester of 2025, respectively, the main author, conducting a first validation, and 12 student groups (19 undergraduate and 7 graduate students) from the Free Software Development course at the University of São Paulo acted as new contributors to the Linux kernel in a broader experiment, used the tool to identify duplications within the Industrial I/O (IIO) subsystem and the AMD Display driver subsystem refactored the code to address the issues, and submitted their proposed fixes as patches to the community maintainers. The students documented their refactoring approaches and experiences interacting with the kernel community throughout this process.
